---
title: "Cultural Moments Marketing Research 2026"
subtitle: "PREPARED FOR KLAVIYO BY DATALILY<br><br><span style='font-size:0.6em; opacity:0.5;'>CONFIDENTIAL — FOR INTERNAL USE ONLY</span>"
format:
  revealjs:
    theme: [default, datalily.scss]
    width: 1920
    height: 1080
    margin: 0.04
    transition: none
    slide-number: false
    controls: true
    controls-layout: edges
    controls-back-arrows: visible
    progress: true
    hash: true
    navigation-mode: linear
    center: false
    auto-stretch: false
    include-after-body: branding.html
    css: deck_custom.css
    embed-resources: true
    
execute:
  echo: false
  warning: false
  message: false
knitr:
  opts_knit:
    root.dir: "/Users/calvinackley/Dropbox/consulting/agent_devel/tests_v2/Klaviyo EMEA - Cultural Moments Marketing 2026/dashboard_processed/dashboard"
  opts_chunk:
    dev: svglite
---

```{r setup}
#| include: false
source("create_cleaned_data.R")

drop_cols <- grep("Q30-Region", colnames(dat_edit), fixed = TRUE)
if (length(drop_cols) > 0) dat_edit <- dat_edit[, -drop_cols]

# Fix Q19 date-encoded labels
q19_cols <- grep("^Q19-", colnames(dat_edit), value = TRUE)
for (cc in q19_cols) {
  dat_edit[[cc]] <- gsub("^46024$", "1-2", dat_edit[[cc]])
  dat_edit[[cc]] <- gsub("^46086$", "3-5", dat_edit[[cc]])
}

library(kableExtra)
library(stringi)
library(cowplot)

bar_color  <- "#530037"
text_color <- "#3f303a"
grid_color <- "#e0dbd6"

make_bar <- function(q_prefix) {
  # Dynamic label sizing based on number of options
  n_opts <- length(get_stub(q_prefix, dat_edit))
  shrink <- if (n_opts <= 5) 2.0
            else if (n_opts <= 7) 1.75
            else if (n_opts <= 9) 1.5
            else if (n_opts <= 11) 1.35
            else 1.2
  calplot_1d(dta = dat_edit, q_prefix = q_prefix, plot_type = "bar",
             input_colors = bar_color, share_min_cutoff = 0.005,
             plot_orient = "vert", ui_params = TRUE, var_dict = var_dict,
             lab_shrinkage = shrink)
}

make_table <- function(q_prefix) {
  info <- var_dict %>% filter(var_prefix == q_prefix)
  qtype <- info$qtype[1]
  if (qtype %in% c("singleselect", "derived")) {
    col <- get_stub(q_prefix, dat_edit)[1]
    dd <- dat_edit %>% filter(!is.na(.data[[col]]))
    tbl <- dd %>% count(Option = .data[[col]]) %>%
      mutate(`%` = round(n / sum(n) * 100)) %>% rename(Count = n) %>% arrange(desc(`%`))
  } else {
    stbs <- get_stub(q_prefix, dat_edit)
    opts <- sub("^.*MULTISELECT \\| ", "", stbs)
    tbl <- tibble(Option = opts,
      Count = vapply(stbs, function(s) sum(dat_edit[[s]] == "Selected", na.rm=TRUE), integer(1)),
      `%` = vapply(stbs, function(s) round(mean(dat_edit[[s]] == "Selected", na.rm=TRUE)*100), numeric(1))
    ) %>% arrange(desc(`%`))
  }
  tbl <- tbl %>% mutate(Option = stri_trans_general(Option, "Latin-ASCII"))
  disp <- tbl; disp$`%` <- paste0(disp$`%`, "%")
  k <- kbl(disp, format = "html", escape = TRUE, align = c("l","r","r")) %>%
    kable_styling(bootstrap_options = c("striped","condensed"), font_size = 18, full_width = TRUE) %>%
    row_spec(0, bold = TRUE, background = "#f0ecf1", color = text_color)
  shades <- scales::col_numeric(c("#FFFFFF","#D4A5C4"), domain = c(0, max(tbl$`%`)))(tbl$`%`)
  column_spec(k, 3, background = shades)
}

make_grid <- function(q_prefix, group_var, color = bar_color) { tryCatch({
  groups <- sort(unique(na.omit(dat_edit[[group_var]])))
  n_groups <- length(groups)

  info <- var_dict %>% filter(var_prefix == q_prefix); qtype <- info$qtype[1]
  if (qtype %in% c("singleselect","derived")) {
    col <- get_stub(q_prefix, dat_edit)[1]; dd <- dat_edit %>% filter(!is.na(.data[[col]]))
    overall <- dd %>% count(Option = .data[[col]]) %>% mutate(Overall = round(n/sum(n)*100)) %>% select(Option, Overall)
    by_g <- dd %>% filter(!is.na(.data[[group_var]])) %>% group_by(.data[[group_var]]) %>% mutate(n_g = n()) %>%
      count(Option = .data[[col]], n_g) %>% mutate(pct = round(n/n_g*100)) %>%
      ungroup() %>% select(!!group_var, Option, pct) %>% pivot_wider(names_from = !!group_var, values_from = pct, values_fill = 0)
    wide <- overall %>% left_join(by_g, by = "Option") %>% arrange(desc(Overall))
  } else {
    stbs <- get_stub(q_prefix, dat_edit); opts <- sub("^.*MULTISELECT [|] ", "", stbs)
    overall <- tibble(Option = opts, Overall = vapply(stbs, function(s) round(mean(dat_edit[[s]]=="Selected",na.rm=TRUE)*100), numeric(1)))
    by_g <- bind_rows(lapply(groups, function(g) {
      d_g <- dat_edit %>% filter(.data[[group_var]] == g)
      tibble(!!group_var := g, Option = opts, pct = vapply(stbs, function(s) round(mean(d_g[[s]]=="Selected",na.rm=TRUE)*100), numeric(1)))
    })) %>% pivot_wider(names_from = !!group_var, values_from = pct, values_fill = 0)
    wide <- overall %>% left_join(by_g, by = "Option") %>% arrange(desc(Overall))
  }
  wide <- wide %>% mutate(Option = stri_trans_general(Option, "Latin-ASCII"))

  n_bars <- nrow(wide)
  max_label_len <- max(nchar(wide$Option), na.rm = TRUE)

  # Complexity score drives all adaptive parameters
  complexity <- n_bars * n_groups * max_label_len / 30

  # Grid layout
  grid_ncol <- if (complexity > 120 & n_groups > 4) 2
               else if (n_groups <= 2) n_groups
               else min(3, n_groups)
  grid_nrow <- ceiling(n_groups / grid_ncol)

  # Wrap width
  wrap_w <- if (complexity > 100) 15
            else if (complexity > 60) 18
            else if (complexity > 30) 22
            else if (n_bars <= 5) 28
            else 22

  # Smart label truncation
  truncate_at <- if (complexity > 120) 35
                 else if (complexity > 80) 45
                 else if (complexity > 50) 55
                 else Inf

  clean_labels <- wide$Option
  if (max_label_len > 40) {
    clean_labels <- gsub("\\s*\\(e\\.g\\..*?\\)", "", clean_labels)
    clean_labels <- gsub("\\s*\\(select.*?\\)", "", clean_labels)
  }
  if (truncate_at < Inf) {
    clean_labels <- ifelse(nchar(clean_labels) > truncate_at,
                           paste0(substr(clean_labels, 1, truncate_at - 3), "..."),
                           clean_labels)
  }
  wide$CleanOption <- clean_labels

  # Font scale
  font_scale <- if (complexity > 120) 0.55
                else if (complexity > 80) 0.65
                else if (complexity > 50) 0.75
                else if (complexity > 30) 0.85
                else 1.0

  lab_sz <- round((if (n_bars <= 5) 12 else if (n_bars <= 8) 10.5 else 8.8) * font_scale)
  pct_sz <- round((if (n_bars <= 5) 4.4 else if (n_bars <= 8) 3.85 else 3.3) * font_scale * 10) / 10
  title_sz <- round(12 * font_scale)
  axis_x_sz <- round(8 * font_scale)
  bw <- if (n_bars <= 5) 0.55 else if (n_bars <= 8) 0.6 else 0.65

  panels <- lapply(groups, function(cc) {
    df <- wide %>% transmute(
      Option = stringr::str_wrap(CleanOption, width = wrap_w),
      pct = .data[[cc]]) %>%
      mutate(Option = forcats::fct_reorder(Option, pct))

    max_val <- max(df$pct, na.rm = TRUE) / 100
    nice_max <- if (max_val <= 0.15) ceiling(max_val * 20) / 20
                else if (max_val <= 0.5) ceiling(max_val * 10) / 10
                else ceiling(max_val * 5) / 5
    nice_max <- min(nice_max, 1); plot_max <- nice_max * 1.15
    brk <- if (nice_max <= 0.2) seq(0, nice_max, 0.05)
           else if (nice_max <= 0.5) seq(0, nice_max, 0.1)
           else seq(0, nice_max, 0.2)

    n_g <- sum(dat_edit[[group_var]] == cc, na.rm = TRUE)

    ggplot(df, aes(x = pct / 100, y = Option)) +
      geom_col(fill = color, width = bw) +
      geom_text(aes(label = paste0(pct, "%")), hjust = -0.1, color = text_color,
                size = pct_sz, fontface = "bold") +
      scale_x_continuous(labels = scales::percent_format(accuracy = 1),
                         limits = c(0, plot_max), breaks = brk, expand = c(0, 0)) +
      labs(title = paste0(cc, " (n=", n_g, ")"), x = NULL, y = NULL) +
      theme_minimal(base_size = 10) +
      theme(
        plot.background = element_rect(fill = "#ffffff", color = NA),
        panel.background = element_blank(),
        panel.grid.major.x = element_line(color = grid_color, linewidth = 0.3),
        panel.grid.major.y = element_blank(),
        panel.grid.minor = element_blank(),
        axis.title = element_blank(),
        axis.text.y = element_text(color = text_color, size = lab_sz, hjust = 1, lineheight = 0.8),
        axis.text.x = element_text(color = text_color, size = axis_x_sz),
        plot.title = element_text(face = "bold", size = title_sz, color = text_color),
        plot.margin = margin(3, 35, 3, 3)
      )
  })

  cowplot::plot_grid(plotlist = panels, ncol = grid_ncol, nrow = grid_nrow)
}, error = function(e) {
  ggplot() + annotate("text", x=.5, y=.5, label = paste("Error:", e$message), size=5, color="#999") + theme_void()
})}

make_xt_table <- function(q_prefix, group_var) {
  info <- var_dict %>% filter(var_prefix == q_prefix)
  qtype <- info$qtype[1]
  groups <- sort(unique(na.omit(dat_edit[[group_var]])))
  if (qtype %in% c("singleselect","derived")) {
    col <- get_stub(q_prefix, dat_edit)[1]
    dd <- dat_edit %>% filter(!is.na(.data[[col]]))
    overall <- dd %>% count(Option = .data[[col]]) %>%
      mutate(Overall = round(n/sum(n)*100)) %>% select(Option, Overall)
    by_g <- dd %>% filter(!is.na(.data[[group_var]])) %>%
      group_by(.data[[group_var]]) %>% mutate(n_g = n()) %>%
      count(Option = .data[[col]], n_g) %>% mutate(pct = round(n/n_g*100)) %>%
      ungroup() %>% select(!!group_var, Option, pct) %>%
      pivot_wider(names_from = !!group_var, values_from = pct, values_fill = 0)
    wide <- overall %>% left_join(by_g, by = "Option") %>% arrange(desc(Overall))
  } else {
    stbs <- get_stub(q_prefix, dat_edit); opts <- sub("^.*MULTISELECT \\| ", "", stbs)
    overall <- tibble(Option = opts,
      Overall = vapply(stbs, function(s) round(mean(dat_edit[[s]]=="Selected",na.rm=TRUE)*100), numeric(1)))
    by_g <- bind_rows(lapply(groups, function(g) {
      d_g <- dat_edit %>% filter(.data[[group_var]] == g)
      tibble(!!group_var := g, Option = opts,
        pct = vapply(stbs, function(s) round(mean(d_g[[s]]=="Selected",na.rm=TRUE)*100), numeric(1)))
    })) %>% pivot_wider(names_from = !!group_var, values_from = pct, values_fill = 0)
    wide <- overall %>% left_join(by_g, by = "Option") %>% arrange(desc(Overall))
  }
  wide <- wide %>% mutate(Option = stri_trans_general(Option, "Latin-ASCII"))
  num_cols <- names(wide)[sapply(wide, is.numeric)]
  disp <- wide; for (cc in num_cols) disp[[cc]] <- paste0(disp[[cc]], "%")
  names(disp)[1] <- ""
  k <- kbl(disp, format = "html", escape = TRUE, align = c("l", rep("r", length(num_cols)))) %>%
    kable_styling(bootstrap_options = c("striped","condensed"), font_size = 14, full_width = TRUE) %>%
    row_spec(0, bold = TRUE, background = "#f0ecf1", color = text_color)
  for (ci in seq_along(num_cols)) {
    vals <- wide[[num_cols[ci]]]; mx <- max(vals, na.rm = TRUE)
    if (mx > 0) { shades <- scales::col_numeric(c("#FFFFFF","#D4A5C4"), domain = c(0, mx))(vals)
      k <- column_spec(k, ci + 1, background = shades) }
  }
  k
}
```


## Research methodology {.q-slide}

:::: {.columns}
::: {.column width="48%"}

::: {.method-section}
**Project goals**

- Understand how B2C marketers plan, execute, and measure cultural moment marketing activations
- Assess readiness and activation plans for the 2026 FIFA World Cup and summer sporting events
- Evaluate AI adoption and its role in speed-to-market for cultural moments
- Measure channel coordination and personalization capabilities
- Identify barriers to faster activation and areas for investment
:::

::: {.method-section}
**Survey methodology**

A 33-question survey was designed by our data scientists and administered to **2,072** B2C marketers via Panoplai across 8 countries.

**Countries:** US (n=404), UK (n=435), France (n=213), Germany (n=207), Spain (n=205), Italy (n=200), Australia (n=203), Singapore (n=205)

**Fielding period:** March–April 2026
:::

:::

::: {.column width="48%"}

::: {.method-section}
**Respondent profile**

B2C marketers with decision-making authority or influence over lifecycle marketing/CRM strategy at organizations with a direct-to-consumer presence.

Respondents were screened for active involvement in marketing strategy, with quotas set by country, vertical, and organization size.
:::

::: {.method-section}
**Crosstab notes**

- **Region:** APAC (n=408), EMEA (n=1,260), United States (n=404)
- **Primary Vertical:** Apparel (n=284), Food/CPG (n=546), Multi-category (n=393), Other (n=849)
- **Size by GMV:** Enterprise (n=730), Non-enterprise (n=1,342)
:::

::: {.method-section}
**Project resources**

[Background analysis and content strategy](){style="color: #4169E1;"}

[Survey questions](){style="color: #4169E1;"}
:::

:::
::::


## Survey demographics: Sales channel model {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q1-")
```
:::
::::


## Survey demographics: Business model {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q2-")
```
:::
::::


## Survey demographics: Decision-making authority {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q3-")
```
:::
::::


## Survey demographics: Organizational role {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q4-")
```
:::
::::


## Survey demographics: Primary vertical {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q5-")
```
:::
::::


## Survey demographics: Organization size by GMV {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q6-")
```
:::
::::


## Research findings {.divider-blue}


## Cultural Moments: Which Moments Matter {.divider-orange}


## Only 27% have a dedicated cultural or real-time marketing team {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q7-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q7-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q7-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q7-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q7-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q7-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q7-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q7-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Final decision-makers are 26% more likely** to have a dedicated cultural marketing team (34% vs. 27% overall), while those who influence decisions lean toward the broader marketing team owning it (34% vs. 26% overall).

2. **Apparel/fashion brands are 33% more likely** to have a dedicated team (36% vs. 27% overall), whereas CPG brands rely more heavily on the broader marketing team (30% vs. 26%).

3. **Enterprise organizations are 26% more likely** to have a dedicated team (34% vs. 27% overall), while non-enterprise firms are 700% more likely to rely on ad hoc approaches (8% vs. 1% enterprise).

4. **In Spain (34%) and Singapore (34%),** dedicated teams are significantly more common, while Germany stands out for shared ownership across teams (31% vs. 22% overall -- 41% higher).

5. **The United States has the highest rate of leadership case-by-case decisions** (26% vs. 19% overall -- 37% higher), and the UK leads in having no single owner (10% vs. 6% overall).

6. **Founders/CEOs are far more likely** to report leadership-driven case-by-case decisions (31% vs. 19% overall), while VPs/Heads of Marketing most commonly report the broader marketing team owning it (40% vs. 26% overall -- 54% higher).

7. **Founders/CEOs are also the most likely** to say cultural moment marketing happens ad hoc (14% vs. 6% overall -- 133% higher), suggesting smaller organizations may lack formalized ownership.
:::
:::
::::

::: {.q-footer}
Q7: Who, in your organization, has primary ownership of cultural moment marketing? (n=2,072)
:::


## 48% of teams activated around both planned and reactive moments in the past year {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q8-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q8-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q8-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q8-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q8-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q8-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q8-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q8-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **APAC marketers are 15% more likely** to activate around both planned and reactive moments (55% vs. 48% overall), while EMEA leans more heavily toward planned-only activations (33% vs. 31%).

2. **Enterprise brands are 17% more likely** to activate around both types (56% vs. 48% overall), while non-enterprise brands are 5x more likely to not activate at all (15% vs. 3% enterprise).

3. **Apparel/fashion brands lead in dual activation** (60% vs. 48% overall -- 25% higher), while "Other" verticals have the highest non-activation rate (16% vs. 11% overall).

4. **Final decision-makers are 15% more likely** to activate around both types (55% vs. 48% overall), while influencers lean toward planned-only moments (40% vs. 31% overall -- 29% higher).

5. **Singapore leads all countries for both-type activation** at 61% (27% higher than overall), while Italy has the highest planned-only rate (43% vs. 31% -- 39% higher).

6. **Male respondents are 31% more likely than female** to focus on planned moments (34% vs. 26%), while female respondents are 44% more likely to report not activating at all (13% vs. 9%).

7. **C-Suite and Directors lead in both-type activation** (54% each vs. 48% overall), while Founders/CEOs have the highest non-activation rate (23% vs. 11% overall -- 109% higher).

8. **VPs/Heads of Marketing heavily favor planned-only activation** (41% vs. 31% overall -- 32% higher).
:::
:::
::::

::: {.q-footer}
Q8: In the past 12 months, has your team intentionally built marketing activations around cultural moments? (n=2,072)
:::


## Regional/national sporting events (42%) and music/entertainment events (41%) lead planned cultural activations {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q9-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q9-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q9-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q9-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q9-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q9-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q9-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q9-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Enterprise brands are significantly more likely** to activate around all major moment types -- 17% more likely for regional sporting (49% vs. 42% overall), 22% more likely for global sporting (45% vs. 37%), and 9% more likely for fashion moments (24% vs. 22%).

2. **Apparel/fashion brands are 123% more likely** to activate around fashion/style moments (49% vs. 22% overall), reflecting strong vertical alignment.

3. **C-Suite executives are 36% more likely** to activate around regional sporting events (57% vs. 42% overall) and 24% more likely for global sporting events (46% vs. 37%).

4. **Male respondents are 12% more likely** to activate around regional sporting (47% vs. 42% overall), while female and male respondents show similar interest in cultural awareness moments (40% vs. 36%).

5. **Final decision-makers are 23% more likely** to activate around fashion moments (27% vs. 22% overall) and 19% more likely for global sporting events (44% vs. 37%).

6. **The United States leads for regional sporting events** at 51% (21% above overall), while the UK leads for cultural awareness moments at 47% (24% above overall).

7. **Germany is 19% above overall for regional sporting** (50%), while Singapore stands out for music/entertainment at 39% and gaming/tech at 9%.
:::
:::
::::

::: {.q-footer}
Q9: Which planned cultural moments has your team activated around in the past 12 months? (n=2,072)
:::


## Match Day: Sporting Events {.divider-orange}


## 45% of teams are planning to activate around the 2026 FIFA World Cup this summer {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q10-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q10-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q10-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q10-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q10-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q10-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q10-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q10-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **EMEA marketers are most likely to activate** around the World Cup (49% vs. 45% overall), while the US leads for not having plans yet (22% vs. 16% -- 38% higher).

2. **C-Suite executives are 33% more likely** to activate around the World Cup (60% vs. 45% overall), while Managers and Founders/CEOs are most likely to lack plans yet (21% and 24% respectively vs. 16%).

3. **Enterprise brands are 22% more likely** to plan World Cup activations (55% vs. 45% overall) and 43% more likely for F1 (30% vs. 21%). Non-enterprise brands are 122% more likely to have no summer plans (20% vs. 9%).

4. **Male respondents are 18% more likely** to plan for the World Cup (53% vs. 45% overall), while female respondents are 31% more likely to have no plans yet (21% vs. 16%).

5. **Australia leads for Commonwealth Games** (40% vs. 13% overall -- 208% higher), France for Roland Garros (36% vs. 11% -- 227% higher) and Tour de France (38% vs. 17% -- 124% higher).

6. **The UK leads for Wimbledon activation** (32% vs. 18% overall -- 78% higher), while APAC leads for F1 planning (33% vs. 21% -- 57% higher).

7. **Multi-category retailers are most likely** to plan for marketing/industry events (40% vs. 33% overall -- 21% higher).
:::
:::
::::

::: {.q-footer}
Q10: Looking ahead to this summer, which events is your team planning to activate around? (n=2,072)
:::


## Time-sensitive offers tied to match results are the top World Cup activation (56%) {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q11-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q11-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q11-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q11-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q11-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q11-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q11-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q11-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Enterprise brands are 9% more likely** to plan time-sensitive offers (61% vs. 56% overall), 8% more likely for curated collections (55% vs. 51%), and 26% more likely to use AI-powered customer service (34% vs. 27%).

2. **Male respondents show similar rates to female** for time-sensitive offers (55% vs. 57%), while males are 17% more likely for personalized messaging (34% vs. 29%).

3. **C-Suite executives show strong engagement** across activation types -- 5% more for time-sensitive offers (59% vs. 56%), 14% for curated collections (58% vs. 51%), and 19% for AI-powered service (32% vs. 27%).

4. **Final decision-makers are 89% more likely** to use AI-powered customer service (34% vs. 18% influencers) and 48% more likely for curated collections (59% vs. 40%).

5. **Germany leads for time-sensitive offers** (66% vs. 56% -- 18% higher), while Spain leads for curated collections (60% vs. 51% -- 18% higher).

6. **Apparel/fashion brands are 37% more likely** to plan curated collections (70% vs. 51% overall), while multi-category retailers lead in AI-powered service (38% vs. 27% -- 41% higher).

7. **The UK leads for increased messaging volume** during match windows (36% vs. 27% overall -- 33% higher).
:::
:::
::::

::: {.q-footer}
Q11: What types of activations are you planning around the World Cup and summer sporting events? (n=2,072)
:::


## International football tournaments delivered the strongest marketing results for 25% of brands {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q12-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q12-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q12-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q12-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q12-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q12-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q12-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q12-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **The US market is dominated by American football** -- 60% cite it as their top performer vs. 18% overall (233% higher), while only 5% cite international football.

2. **EMEA strongly favors international football tournaments** (30% vs. 25% overall) and regional leagues (15% vs. 11% -- 36% higher).

3. **APAC marketers are the most likely to cite motorsport** as top-performing (19% vs. 11% overall -- 73% higher) and cricket (7% vs. 2% -- 250% higher).

4. **Australia leads for cricket at 12%** (500% above the 2% overall) and motorsport at 20% (82% above overall), reflecting distinct regional sports preferences.

5. **Spain leads for international football** (35%), while the UK leads for regional leagues (16%).

6. **C-Suite executives are 45% more likely** to cite motorsport (16% vs. 11% overall) and show broader distribution across sports.

7. **Enterprise brands are 12% more likely** to cite international football (28% vs. 25% overall).
:::
:::
::::

::: {.q-footer}
Q12: Which sporting event delivered the strongest marketing results for your brand in the past 12 months? (n=2,072)
:::


## Only 38% of teams are fully ready with plans, assets, and triggers for the 2026 World Cup {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q13-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q13-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q13-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q13-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q13-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q13-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q13-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q13-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Final decision-makers are 16% more likely** to be fully ready (44% vs. 38% overall), while influencers are more likely to still be in planning (47% "on the squad" vs. 45%).

2. **Enterprise brands are 21% more likely** to be Starting XI ready (46% vs. 38% overall), while non-enterprise are more likely to still be in training (16% vs. 10%).

3. **Italy (47%) and Germany (46%) lead for full readiness,** while Australia and Singapore lag with the highest "on the squad" rates (55% and 56% respectively vs. 45% overall).

4. **Apparel/fashion brands lead in full readiness** (48% vs. 38% overall -- 26% higher), while CPG and Other verticals are more likely to still be building assets.

5. **Founders/CEOs report the highest full readiness** (50% vs. 38% overall -- 32% higher), likely due to control over shorter approval chains. Directors are most likely to still be building (51% vs. 45% overall).

6. **APAC has the highest "on the squad" rate** (55% vs. 45% overall) and the lowest full readiness (31% vs. 38% -- 18% below), suggesting more preparation is still needed.

7. **Female respondents are more likely** to still be in training (17% vs. 10% male), while male respondents are 21% more likely to be fully ready (41% vs. 34%).
:::
:::
::::

::: {.q-footer}
Q13: How prepared is your team to activate in time during the 2026 World Cup? (n=2,072)
:::


## 88% of teams plan to increase marketing budget for summer sporting events {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q14-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q14-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q14-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q14-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q14-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q14-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q14-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q14-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Final decision-makers are 32% more likely** to plan significant budget increases of >50% (25% vs. 19% overall), while influencers are 60% more likely to keep the same budget with different allocation (16% vs. 10%).

2. **Italy leads in significant (>50%) budget increases** at 30% (58% above the 19% overall), while Spain leads in substantial increases (46% vs. 39%).

3. **EMEA leads for substantial increases** (41% vs. 39% overall), while APAC leans toward somewhat increases (38% vs. 30% overall -- 27% higher).

4. **Founders/CEOs are the most aggressive,** with 30% planning >50% increases (58% above overall), while Managers are most conservative (11% for >50%, and 15% for same-budget allocation).

5. **Male respondents are 13% more likely** to plan substantial increases (44% vs. 39% overall), while female respondents lean toward moderate increases (33% vs. 30%).

6. **Apparel/fashion and multi-category retailers** both lead in significant increases (24% each vs. 19% overall -- 26% higher).

7. **Australia stands out for favoring moderate increases** (43% "somewhat" vs. 30% overall -- 43% higher), suggesting more cautious budget approaches.
:::
:::
::::

::: {.q-footer}
Q14: Will your team increase its marketing budget for summer sporting events compared to your typical always-on spend? (n=2,072)
:::


## Speed and Stakes {.divider-orange}


## 45% plan to use AI to personalize messaging based on fan preferences and match outcomes {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q15-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q15-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q15-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q15-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q15-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q15-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q15-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q15-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **C-Suite executives are 16% more likely** to plan AI personalization (52% vs. 45% overall) and 18% more likely to plan AI-powered campaign production (39% vs. 33%).

2. **Enterprise brands show similar rates** for AI personalization (44% vs. 45% overall) but are 23% more likely to use AI for faster campaign production (37% vs. 30% non-enterprise).

3. **VPs/Heads of Marketing are 11% more likely** to plan AI personalization (50% vs. 45% overall) and 29% more likely for AI customer service (31% vs. 24%).

4. **Final decision-makers are 86% more likely** to use AI for faster production (41% vs. 22% influencers), suggesting speed is a top priority for those with direct control.

5. **Spain leads for AI-driven campaign production** (39% vs. 33% overall -- 18% higher), while the US leads for AI customer service (27%).

6. **Male respondents are 10% more likely** to plan AI personalization (46% vs. 42% female) and 6% more likely for faster AI production (34% vs. 32% female).

7. **Multi-category retailers lead for AI personalization** (50% vs. 45% overall -- 11% higher).
:::
:::
::::

::: {.q-footer}
Q15: Are you planning to use AI specifically to power your summer sporting activations? (n=2,072)
:::


## 38% of teams prepare activations 3-6 months before a planned cultural moment {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q16-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q16-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q16-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q16-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q16-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q16-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q16-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q16-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **France leads in very early preparation** -- 35% prepare more than 6 months ahead (59% above the 22% overall), while Singapore is also strong at 32%.

2. **Spain leads for 3-6 month preparation** at 48% (26% above the 38% overall), indicating strong mid-range planning discipline.

3. **The United States has the highest rate of "week of" preparation** (4% vs. 2% overall -- 100% higher), suggesting more reactive planning.

4. **Enterprise brands are 18% more likely** to prepare >6 months ahead (26% vs. 22% overall), while non-enterprise brands are more likely to prepare just 2-4 weeks before (10% vs. 8%).

5. **Apparel/fashion brands are 18% more likely** to start >6 months ahead (26% vs. 22% overall), aligning with the longer product development cycles in fashion.

6. **Founders/CEOs have the highest rate of last-minute preparation** -- 4% prepare "the week of" (100% above overall) and 2% are still finalizing when events start.

7. **APAC has the highest rate of >6 months preparation** (26% vs. 22% overall -- 18% higher).
:::
:::
::::

::: {.q-footer}
Q16: How far ahead of a planned cultural moment (e.g. World Cup, Wimbledon) does your team typically have the activation ready to launch? (n=2,072)
:::


## 41% of teams can launch a reactive campaign within 6 hours of a viral moment {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q17-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q17-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q17-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q17-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q17-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q17-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q17-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q17-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **US marketers are 56% more likely** to respond within 2 hours (25% vs. 16% overall), far outpacing every other country -- France is lowest at just 7%.

2. **Final decision-makers are 19% more likely** to respond within 2 hours (19% vs. 16% overall), while influencers are 36% more likely to take 48+ hours (15% vs. 11% overall).

3. **Founders/CEOs are 50% more likely** to respond within 2 hours (24% vs. 16% overall), likely due to fewer approval layers.

4. **Germany stands out for the 12-hour window** (30% vs. 22% overall -- 36% higher), suggesting structured but efficient response processes.

5. **Managers are the slowest to respond** -- 17% take 48+ hours (55% above the 11% overall) and only 11% respond within 2 hours (31% below overall).

6. **France has the highest rate of >48 hour response** (10% vs. 6% overall -- 67% higher), alongside the lowest <2 hour rate (7%).

7. **APAC and EMEA are similar in overall speed distribution,** while the US concentrates more at the fastest end.
:::
:::
::::

::: {.q-footer}
Q17: When an unexpected viral moment or cultural flashpoint hits, how quickly can your team get a campaign live? (n=2,072)
:::


## 37% launched their most successful cultural activation within 1-3 days of spotting the opportunity {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q18-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q18-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q18-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q18-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q18-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q18-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q18-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q18-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **The US leads for under-24-hour launches** (26% vs. 17% overall -- 53% higher), while France is slowest with 15% taking more than 2 weeks (88% above the 8% overall).

2. **Final decision-makers are 24% more likely** to launch within 24 hours (21% vs. 17% overall), while influencers are 38% more likely to take more than 2 weeks (11% vs. 8%).

3. **Founders/CEOs are 53% more likely** to launch under 24 hours (26% vs. 17% overall), and 39% less likely to take 4-7 days (14% vs. 23% overall).

4. **VPs/Heads of Marketing skew toward the 4-7 day window** (35% vs. 23% overall -- 52% higher), suggesting more structured processes with approval gates.

5. **Spain has the highest 1-3 day rate** (40% vs. 37% overall), while France shows notable 4-7 day preference (30% vs. 23% -- 30% higher).

6. **Multi-category retailers are 18% more likely** to launch in under 24 hours (20% vs. 17% overall), while CPG brands cluster in 1-3 days (38% vs. 37%).

7. **Enterprise brands take slightly longer** -- 15% take 1-2 weeks (15% above the 13% overall) and 10% more than 2 weeks (25% above overall).
:::
:::
::::

::: {.q-footer}
Q18: Thinking about your most successful cultural moment activation in the past 12 months: how long did it take from spotting the opportunity to launching the campaign? (n=2,072)
:::


## 47% of teams missed 1-2 cultural moments in the past year because they couldn't move fast enough {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q19-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q19-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q19-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q19-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q19-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q19-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q19-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q19-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Spain has the highest miss rate** -- 56% missed 1-2 moments (19% above the 47% overall) and only 26% missed none (24% below the 34% overall).

2. **VPs/Heads of Marketing miss the most** -- 55% missed 1-2 moments (17% above overall) and only 26% missed none (24% below overall).

3. **The US and UK have the highest "none missed" rates** (39% and 37% respectively vs. 34% overall), suggesting faster or more selective approaches.

4. **Enterprise brands are more likely to miss 3-5 moments** (17% vs. 14% non-enterprise), suggesting ambition-vs-execution gaps at larger organizations.

5. **Founders/CEOs have the highest rate of missing 5+ moments** (7% vs. 4% overall -- 75% higher), possibly due to overcommitting without sufficient team bandwidth.

6. **Singapore (56%) and Spain (56%) both significantly over-index** on the 1-2 miss rate.

7. **The UK has the highest 5+ miss rate** (7% vs. 4% overall -- 75% higher).
:::
:::
::::

::: {.q-footer}
Q19: In the past 12 months, how many cultural moments did your team miss because you couldn't move fast enough? (n=2,072)
:::


## 53% of marketers attribute 10-20% of total marketing revenue to cultural moment activations {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q20-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q20-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q20-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q20-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q20-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q20-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q20-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q20-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Final decision-makers are 14% more likely** to attribute >20% of revenue to cultural moments (24% vs. 21% overall), suggesting those with budget control see higher returns.

2. **Apparel/fashion brands are 29% more likely** to report >20% revenue from cultural moments (27% vs. 21% overall), the highest of any vertical.

3. **Enterprise brands are 14% more likely** to report >20% revenue share (24% vs. 21% overall).

4. **Spain (25%) and Singapore (26%) lead for >20% revenue share,** while Australia is lowest at 17%.

5. **Directors and VPs/Heads of Marketing cluster at 10-20%** (60% and 59% respectively vs. 53% overall -- 11-13% higher), with less variance than other roles.

6. **Italy has the lowest rate of not measuring separately** (3% vs. 10% overall -- 70% lower), suggesting more disciplined attribution.

7. **Founders/CEOs are 50% more likely** to not measure revenue separately (15% vs. 10% overall), suggesting less formal measurement among smaller firms.

8. **The US leads for not having a formal measurement approach** (11% "don't measure"), while EMEA has the strongest 10-20% concentration (54%).
:::
:::
::::

::: {.q-footer}
Q20: Approximately what share of your total marketing revenue comes from cultural moment activations vs. routine calendar marketing? (n=2,072)
:::


## Channels, Data, and Personalization {.divider-orange}


## 63% assess each cultural moment case-by-case based on brand fit and audience relevance {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q21-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q21-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q21-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q21-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q21-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q21-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q21-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q21-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Spain leads for case-by-case assessment** (73% vs. 63% overall -- 16% higher), while France and Italy lead for clear brand guidelines (33% each vs. 28%).

2. **Final decision-makers are 14% more likely** to have clear brand guidelines (32% vs. 28% overall), while influencers lean more toward case-by-case (67% vs. 63%).

3. **Enterprise brands are 21% more likely** to have clear guidelines (34% vs. 28% overall), while non-enterprise are more likely to rely on gut calls (4% vs. 1%).

4. **Founders/CEOs are the most likely** to report making gut calls (6% vs. 3% overall -- 100% higher), and the most likely to have brand guidelines (33% vs. 28%).

5. **Directors are the strongest case-by-case assessors** (71% vs. 63% overall -- 13% higher), suggesting a process-driven approach.

6. **Apparel/fashion brands are 18% more likely** to have clear brand guidelines (33% vs. 28% overall), aligning with stronger brand identity positioning.

7. **The UK has the highest "gut call" rate** (6% vs. 3% overall -- 100% higher), and the highest competitor-following rate (7%).
:::
:::
::::

::: {.q-footer}
Q21: How does your team decide whether or not it has a credible reason to participate in a cultural moment? (n=2,072)
:::


## Social media dominates cultural moment activations, cited by 46% as the top-performing channel {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q22-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q22-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q22-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q22-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q22-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q22-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q22-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q22-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **The UK leads for social media as the top channel** at 58%, while Spain dramatically favors WhatsApp (22% vs. 10% overall -- 120% higher) and has the lowest social media reliance (25%).

2. **The US has the highest SMS preference** (9% vs. 5% overall -- 80% higher), while WhatsApp is only at 3% in the US.

3. **EMEA leads for WhatsApp** (13% vs. 10% overall -- 30% higher) and influencer partnerships (12% vs. 10%), while the US leads for SMS (9% vs. 5%).

4. **Italy has the highest influencer/creator partnership preference** at 16% (60% above the 10% overall).

5. **VPs/Heads of Marketing lead for influencer partnerships** (16% vs. 10% overall -- 60% higher), while C-Suite favors WhatsApp (14% vs. 10%).

6. **Enterprise brands are 43% more likely** to favor advertising (10% vs. 7% overall), while non-enterprise lean more toward social media (48% vs. 43% enterprise).

7. **Apparel/fashion brands are the strongest social media advocates** (54% vs. 46% overall -- 17% higher).
:::
:::
::::

::: {.q-footer}
Q22: Which channel delivers the best results for your cultural moment activations? (n=2,072)
:::


## Only 40% report fully coordinated channel activation during cultural moments {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q23-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q23-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q23-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q23-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q23-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q23-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q23-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q23-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Final decision-makers are 15% more likely** to report full coordination (46% vs. 40% overall), while influencers are more likely to say channels are "mostly coordinated" (56% vs. 51%).

2. **Enterprise brands are 13% more likely** to be fully coordinated (45% vs. 40% overall), while non-enterprise are 60% more likely to have independently operating channels (8% vs. 5%).

3. **Apparel/fashion brands lead in full coordination** (50% vs. 40% overall -- 25% higher), while "Other" verticals have the highest independent channel rate (9% vs. 7%).

4. **Founders/CEOs and VPs/Heads of Marketing** both report the highest full coordination (47% each vs. 40% overall -- 18% higher).

5. **France has the highest independent channel rate** (9% vs. 7% overall -- 29% higher), while Australia has the lowest (3%).

6. **The US leads in full coordination** (43% vs. 40% overall), while EMEA has the highest partial coordination (50%).

7. **Female respondents are more likely to be unsure** about coordination (3% vs. 1% male), suggesting potential visibility gaps in cross-channel planning.
:::
:::
::::

::: {.q-footer}
Q23: In your opinion, how coordinated are your channels when you activate around a cultural moment? (n=2,072)
:::


## 55% are only "fairly confident" they reach the right customers during cultural activations {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q24-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q24-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q24-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q24-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q24-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q24-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q24-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q24-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Final decision-makers are 17% more likely** to be very confident (48% vs. 41% overall), while influencers skew heavily toward fairly confident (63% vs. 55% overall -- 15% higher).

2. **The US leads for very confident** (48% vs. 41% overall -- 17% higher), while Singapore is least confident (34% "very" -- 17% below overall).

3. **Enterprise brands are 20% more likely** to be very confident (49% vs. 41% overall), while non-enterprise are more likely to report low confidence (5% vs. 3%).

4. **C-Suite executives are the most confident** -- 50% report "very confident" (22% above the 41% overall), while Directors are the least confident of leadership roles (31% "very").

5. **Apparel/fashion brands lead in very confident ratings** (49% vs. 41% overall -- 20% higher), while "Other" verticals have the highest not-very-confident rate (6% vs. 4%).

6. **APAC skews toward fairly confident** (60% vs. 55% overall), while the US leads for very confident (48%).

7. **Female respondents are 100% more likely** to report "not very confident" (6% vs. 3% male), suggesting potential gaps in data access or personalization tools.
:::
:::
::::

::: {.q-footer}
Q24: When you activate around a cultural moment, how confident are you that your team is reaching the right customers with the right message? (n=2,072)
:::


## The AI Advantage {.divider-orange}


## AI-assisted content creation is the #1 enabler (35%) for halving cultural moment launch times {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q25-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q25-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q25-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q25-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q25-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q25-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q25-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q25-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **France stands out dramatically** -- 50% cite AI-assisted content creation (43% above the 35% overall), the highest of any country.

2. **Australia leads for needing streamlined approvals** (23% vs. 17% overall -- 35% higher), while APAC as a region also over-indexes on approvals (20% vs. 17%).

3. **Male respondents are 14% more likely** to prioritize AI content creation (40% vs. 35% overall), while female respondents are 10% more likely to prioritize real-time data (33% vs. 30%).

4. **The US leads for needing pre-built templates** (16% vs. 13% overall -- 23% higher).

5. **Influencers are 62% more likely** to need streamlined approvals (21% vs. 13% decision-makers), while decision-makers prioritize real-time data (34% vs. 26% -- 31% higher).

6. **Managers are the most likely** to need streamlined approvals (19% vs. 17% overall) and clearer ownership (7% vs. 5% overall -- 40% higher).

7. **Multi-category retailers lead for needing real-time data** (36% vs. 30% overall -- 20% higher).

8. **Australia is the only country** where real-time data (33%) outranks AI content creation (27%) as the top need.
:::
:::
::::

::: {.q-footer}
Q25: What would most help your team halve the time it takes to launch a cultural moment activation? (n=2,072)
:::


## Content generation (42%) leads current AI use, with send-time optimization (34%) and segmentation (33%) close behind {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q26-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q26-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q26-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q26-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q26-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q26-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q26-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q26-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **APAC leads in every AI use case** -- 47% for content generation (12% above overall), 37% for segmentation (12% higher), and 42% for send-time optimization (24% higher).

2. **Enterprise brands are 5% more likely** to use AI for content generation (44% vs. 42%), 15% more for segmentation (38% vs. 33%), and 25% more for AI customer service (25% vs. 20%).

3. **C-Suite is the biggest AI adopter** -- 36% more likely to use segmentation (45% vs. 33%), 12% more for send-time optimization (38% vs. 34%), and 20% more for AI customer service (24% vs. 20%).

4. **The US and UK have the highest AI non-adoption** (14% and 13% respectively vs. 8% overall -- 75% and 63% higher), while Italy and Singapore are lowest (3% each).

5. **Singapore leads for content generation** (50% vs. 42% overall -- 19% higher) and send-time optimization (44% vs. 34% -- 29% higher).

6. **Male respondents are 32% more likely** to use segmentation (37% vs. 28% female) and 9% more for send-time optimization (35% vs. 32% female).

7. **Multi-category retailers lead in building full campaigns** from brief (24% vs. 19% overall -- 26% higher).
:::
:::
::::

::: {.q-footer}
Q26: How does your team currently use AI or automation for cultural moment activations? (n=2,072)
:::


## 79% are positive about or already exploring AI-driven "vibe marketing" for cultural activations {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q27-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q27-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q27-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q27-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q27-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q27-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q27-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q27-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **APAC is the most positive region** -- 60% positive (11% above the 54% overall), while the US is the most skeptical (10% vs. 8% overall).

2. **Final decision-makers are 24% more likely** to already be doing or exploring vibe marketing (31% vs. 25% overall), while influencers are more broadly positive (59% vs. 54%).

3. **Founders/CEOs show the sharpest polarization** -- 31% are already doing it (24% above overall), but 14% are skeptical (75% above the 8% overall).

4. **Directors are the most positive** (64% vs. 54% overall -- 19% higher) and the least skeptical (4%).

5. **Enterprise brands are 20% more likely** to already be doing it (30% vs. 25% overall) and 44% less likely to be skeptical (5% vs. 9% non-enterprise).

6. **Singapore leads for positivity** (63% vs. 54% overall -- 17% higher), while France has the highest unsure rate (20% vs. 13% overall -- 54% higher).

7. **Apparel/fashion brands are 24% more likely** to already be doing it (31% vs. 25% overall), while "Other" verticals have the highest skepticism (10% vs. 8%).

8. **Female respondents are 23% more likely** to be unsure (16% vs. 13% overall) and 29% more likely to be skeptical (9% vs. 7% male).
:::
:::
::::

::: {.q-footer}
Q27: Some teams now define the outcome they want and let AI generate the content, audience, and launch the activation automatically - sometimes called "vibe marketing." How do you feel about this? (n=2,072)
:::


## Performance and Confidence {.divider-orange}


## 43% of teams primarily measure cultural moment success through brand building metrics {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q28-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q28-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q28-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q28-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q28-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q28-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q28-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q28-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **The US stands out as the most commercial** -- 45% measure both commercial and brand (45% above the 31% overall), and only 36% focus on brand alone (16% below the 43% overall).

2. **France is the most brand-focused** at 55% (28% above the 43% overall), while Germany leads for short-term commercial metrics (33% vs. 24% -- 38% higher).

3. **VPs/Heads of Marketing are the most brand-focused** (54% vs. 43% overall -- 26% higher), while Founders/CEOs are most likely to focus on short-term commercial (30% vs. 24% -- 25% higher).

4. **EMEA is the most commercially focused region** -- 26% short-term commercial (vs. 24% overall), while the US leads for balanced measurement at 45%.

5. **Founders/CEOs have the highest rate** of no formal measurement (4% vs. 2% overall -- 100% higher).

6. **Enterprise brands and non-enterprise brands** show similar measurement profiles, with enterprise slightly more likely to measure both (33% vs. 30%).

7. **CPG brands lead for brand-building focus** (47% vs. 43% overall), while apparel/fashion brands have the most balanced approach (31% both).
:::
:::
::::

::: {.q-footer}
Q28: What is your primary measure of success for cultural moment activations? (n=2,072)
:::


## 37% say cultural moment activations outperform routine calendar marketing like Black Friday {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q29-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q29-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q29-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q29-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q29-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q29-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q29-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q29-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **France leads with 46% saying cultural moments outperform** (24% above the 37% overall), while the UK and US are tied at the lowest (33% each).

2. **Final decision-makers are 11% more likely** to say cultural moments outperform (41% vs. 37% overall), while influencers see more parity (62% "about the same" vs. 56% overall).

3. **Enterprise brands are 14% more likely** to report outperformance (42% vs. 37% overall), while non-enterprise are more likely to see parity (60% vs. 51%).

4. **Apparel/fashion brands are 19% more likely** to see outperformance (44% vs. 37% overall), the highest of any vertical.

5. **Australia has the highest underperformance rate** (11% vs. 7% overall -- 57% higher).

6. **VPs/Heads of Marketing and C-Suite** are the most likely to report outperformance (41% and 39% respectively vs. 37% overall).

7. **Male respondents are 15% more likely** to see outperformance (39% vs. 34% female), while female respondents lean toward "about the same" (59% vs. 54%).

8. **Italy sees the most parity** -- 62% say about the same (11% above overall), with one of the lowest outperform rates (35%).
:::
:::
::::

::: {.q-footer}
Q29: Compared to your routine calendar marketing (e.g. Black Friday, Cyber Monday, holiday), how do cultural moment activations perform? (n=2,072)
:::


## 76% of teams report more creative freedom during cultural moment activations than routine marketing {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q30-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q30-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q30-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q30-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q30-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q30-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q30-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q30-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Final decision-makers are 24% more likely** to report significantly more freedom (31% vs. 25% overall), while influencers are more likely to say "about the same" (21% vs. 19%).

2. **Spain leads for significantly more freedom** (32% vs. 25% overall -- 28% higher) and Singapore for somewhat more freedom (60% vs. 51% overall -- 18% higher).

3. **Apparel/fashion brands lead in significantly more freedom** (33% vs. 25% overall -- 32% higher), reflecting the creative culture of fashion marketing.

4. **Founders/CEOs report the most experimentation** (32% significantly more vs. 25% overall -- 28% higher), but also the most "about the same" responses (21%).

5. **Directors lean toward consistent treatment** -- 60% say somewhat more (vs. 51% overall -- 18% higher) but only 18% say significantly more.

6. **The US and Australia are most conservative** -- 23% and 24% "about the same" respectively (vs. 19% overall -- 21-26% higher).

7. **Enterprise brands are slightly more cautious** (7% somewhat less vs. 4% non-enterprise), but also more likely to be fully coordinated (27% significantly more vs. 24%).
:::
:::
::::

::: {.q-footer}
Q30: Compared to routine marketing activations, how much creative freedom does your team typically have when activating around cultural moments? (n=2,072)
:::


## Survey demographics: Respondent age distribution {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q31-")
```
:::
::::


## Survey demographics: Respondent gender {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q32-")
```
:::
::::


## Survey demographics: Respondent country {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q33-")
```
:::
::::


## Thank you {.thankyou}

HELLO@DATALILY.COM
