---
title: "Cultural Moments Marketing Research 2026"
subtitle: "PREPARED FOR KLAVIYO BY DATALILY<br><br><span style='font-size:0.6em; opacity:0.5;'>CONFIDENTIAL — FOR INTERNAL USE ONLY</span>"
format:
  revealjs:
    theme: [default, datalily.scss]
    width: 1920
    height: 1080
    margin: 0.08
    transition: none
    slide-number: false
    controls: true
    controls-layout: edges
    controls-back-arrows: visible
    progress: true
    hash: true
    navigation-mode: linear
    center: false
    auto-stretch: false
    include-after-body: branding.html
    css: deck_custom.css
    embed-resources: true
    
execute:
  echo: false
  warning: false
  message: false
knitr:
  opts_knit:
    root.dir: "/Users/calvinackley/Dropbox/consulting/agent_devel/tests_v2/Klaviyo EMEA - Cultural Moments Marketing 2026/dashboard_processed/dashboard"
  opts_chunk:
    dev: svglite
---

```{r setup}
#| include: false
source("create_cleaned_data.R")

drop_cols <- grep("Q30-Region", colnames(dat_edit), fixed = TRUE)
if (length(drop_cols) > 0) dat_edit <- dat_edit[, -drop_cols]

# Fix Q19 date-encoded labels
q19_cols <- grep("^Q19-", colnames(dat_edit), value = TRUE)
for (cc in q19_cols) {
  dat_edit[[cc]] <- gsub("^46024$", "1-2", dat_edit[[cc]])
  dat_edit[[cc]] <- gsub("^46086$", "3-5", dat_edit[[cc]])
}

library(kableExtra)
library(stringi)
library(cowplot)

bar_color  <- "#530037"
text_color <- "#3f303a"
grid_color <- "#e0dbd6"

make_bar <- function(q_prefix) {
  # Dynamic label sizing based on number of options
  n_opts <- length(get_stub(q_prefix, dat_edit))
  shrink <- if (n_opts <= 5) 2.0
            else if (n_opts <= 7) 1.75
            else if (n_opts <= 9) 1.5
            else if (n_opts <= 11) 1.35
            else 1.2
  calplot_1d(dta = dat_edit, q_prefix = q_prefix, plot_type = "bar",
             input_colors = bar_color, share_min_cutoff = 0.005,
             plot_orient = "vert", ui_params = TRUE, var_dict = var_dict,
             lab_shrinkage = shrink)
}

make_table <- function(q_prefix) {
  info <- var_dict %>% filter(var_prefix == q_prefix)
  qtype <- info$qtype[1]
  if (qtype %in% c("singleselect", "derived")) {
    col <- get_stub(q_prefix, dat_edit)[1]
    dd <- dat_edit %>% filter(!is.na(.data[[col]]))
    tbl <- dd %>% count(Option = .data[[col]]) %>%
      mutate(`%` = round(n / sum(n) * 100)) %>% rename(Count = n) %>% arrange(desc(`%`))
  } else {
    stbs <- get_stub(q_prefix, dat_edit)
    opts <- sub("^.*MULTISELECT \\| ", "", stbs)
    tbl <- tibble(Option = opts,
      Count = vapply(stbs, function(s) sum(dat_edit[[s]] == "Selected", na.rm=TRUE), integer(1)),
      `%` = vapply(stbs, function(s) round(mean(dat_edit[[s]] == "Selected", na.rm=TRUE)*100), numeric(1))
    ) %>% arrange(desc(`%`))
  }
  tbl <- tbl %>% mutate(Option = stri_trans_general(Option, "Latin-ASCII"))
  disp <- tbl; disp$`%` <- paste0(disp$`%`, "%")
  k <- kbl(disp, format = "html", escape = TRUE, align = c("l","r","r")) %>%
    kable_styling(bootstrap_options = c("striped","condensed"), font_size = 18, full_width = TRUE) %>%
    row_spec(0, bold = TRUE, background = "#f0ecf1", color = text_color)
  shades <- scales::col_numeric(c("#FFFFFF","#D4A5C4"), domain = c(0, max(tbl$`%`)))(tbl$`%`)
  column_spec(k, 3, background = shades)
}

make_grid <- function(q_prefix, group_var, color = bar_color) { tryCatch({
  groups <- sort(unique(na.omit(dat_edit[[group_var]])))
  n_groups <- length(groups)

  info <- var_dict %>% filter(var_prefix == q_prefix); qtype <- info$qtype[1]
  if (qtype %in% c("singleselect","derived")) {
    col <- get_stub(q_prefix, dat_edit)[1]; dd <- dat_edit %>% filter(!is.na(.data[[col]]))
    overall <- dd %>% count(Option = .data[[col]]) %>% mutate(Overall = round(n/sum(n)*100)) %>% select(Option, Overall)
    by_g <- dd %>% filter(!is.na(.data[[group_var]])) %>% group_by(.data[[group_var]]) %>% mutate(n_g = n()) %>%
      count(Option = .data[[col]], n_g) %>% mutate(pct = round(n/n_g*100)) %>%
      ungroup() %>% select(!!group_var, Option, pct) %>% pivot_wider(names_from = !!group_var, values_from = pct, values_fill = 0)
    wide <- overall %>% left_join(by_g, by = "Option") %>% arrange(desc(Overall))
  } else {
    stbs <- get_stub(q_prefix, dat_edit); opts <- sub("^.*MULTISELECT [|] ", "", stbs)
    overall <- tibble(Option = opts, Overall = vapply(stbs, function(s) round(mean(dat_edit[[s]]=="Selected",na.rm=TRUE)*100), numeric(1)))
    by_g <- bind_rows(lapply(groups, function(g) {
      d_g <- dat_edit %>% filter(.data[[group_var]] == g)
      tibble(!!group_var := g, Option = opts, pct = vapply(stbs, function(s) round(mean(d_g[[s]]=="Selected",na.rm=TRUE)*100), numeric(1)))
    })) %>% pivot_wider(names_from = !!group_var, values_from = pct, values_fill = 0)
    wide <- overall %>% left_join(by_g, by = "Option") %>% arrange(desc(Overall))
  }
  wide <- wide %>% mutate(Option = stri_trans_general(Option, "Latin-ASCII"))

  n_bars <- nrow(wide)
  max_label_len <- max(nchar(wide$Option), na.rm = TRUE)

  # Complexity score drives all adaptive parameters
  complexity <- n_bars * n_groups * max_label_len / 30

  # Grid layout
  grid_ncol <- if (complexity > 120 & n_groups > 4) 2
               else if (n_groups <= 2) n_groups
               else min(3, n_groups)
  grid_nrow <- ceiling(n_groups / grid_ncol)

  # Wrap width
  wrap_w <- if (complexity > 100) 15
            else if (complexity > 60) 18
            else if (complexity > 30) 22
            else if (n_bars <= 5) 28
            else 22

  # Smart label truncation
  truncate_at <- if (complexity > 120) 35
                 else if (complexity > 80) 45
                 else if (complexity > 50) 55
                 else Inf

  clean_labels <- wide$Option
  if (max_label_len > 40) {
    clean_labels <- gsub("\\s*\\(e\\.g\\..*?\\)", "", clean_labels)
    clean_labels <- gsub("\\s*\\(select.*?\\)", "", clean_labels)
  }
  if (truncate_at < Inf) {
    clean_labels <- ifelse(nchar(clean_labels) > truncate_at,
                           paste0(substr(clean_labels, 1, truncate_at - 3), "..."),
                           clean_labels)
  }
  wide$CleanOption <- clean_labels

  # Font scale
  font_scale <- if (complexity > 120) 0.55
                else if (complexity > 80) 0.65
                else if (complexity > 50) 0.75
                else if (complexity > 30) 0.85
                else 1.0

  lab_sz <- round((if (n_bars <= 5) 12 else if (n_bars <= 8) 10.5 else 8.8) * font_scale)
  pct_sz <- round((if (n_bars <= 5) 4.4 else if (n_bars <= 8) 3.85 else 3.3) * font_scale * 10) / 10
  title_sz <- round(12 * font_scale)
  axis_x_sz <- round(8 * font_scale)
  bw <- if (n_bars <= 5) 0.55 else if (n_bars <= 8) 0.6 else 0.65

  panels <- lapply(groups, function(cc) {
    df <- wide %>% transmute(
      Option = stringr::str_wrap(CleanOption, width = wrap_w),
      pct = .data[[cc]]) %>%
      mutate(Option = forcats::fct_reorder(Option, pct))

    max_val <- max(df$pct, na.rm = TRUE) / 100
    nice_max <- if (max_val <= 0.15) ceiling(max_val * 20) / 20
                else if (max_val <= 0.5) ceiling(max_val * 10) / 10
                else ceiling(max_val * 5) / 5
    nice_max <- min(nice_max, 1); plot_max <- nice_max * 1.15
    brk <- if (nice_max <= 0.2) seq(0, nice_max, 0.05)
           else if (nice_max <= 0.5) seq(0, nice_max, 0.1)
           else seq(0, nice_max, 0.2)

    n_g <- sum(dat_edit[[group_var]] == cc, na.rm = TRUE)

    ggplot(df, aes(x = pct / 100, y = Option)) +
      geom_col(fill = color, width = bw) +
      geom_text(aes(label = paste0(pct, "%")), hjust = -0.1, color = text_color,
                size = pct_sz, fontface = "bold") +
      scale_x_continuous(labels = scales::percent_format(accuracy = 1),
                         limits = c(0, plot_max), breaks = brk, expand = c(0, 0)) +
      labs(title = paste0(cc, " (n=", n_g, ")"), x = NULL, y = NULL) +
      theme_minimal(base_size = 10) +
      theme(
        plot.background = element_rect(fill = "#ffffff", color = NA),
        panel.background = element_blank(),
        panel.grid.major.x = element_line(color = grid_color, linewidth = 0.3),
        panel.grid.major.y = element_blank(),
        panel.grid.minor = element_blank(),
        axis.title = element_blank(),
        axis.text.y = element_text(color = text_color, size = lab_sz, hjust = 1, lineheight = 0.8),
        axis.text.x = element_text(color = text_color, size = axis_x_sz),
        plot.title = element_text(face = "bold", size = title_sz, color = text_color, margin = margin(0, 0, 4, 0)),
        plot.margin = margin(8, 35, 3, 3)
      )
  })

  cowplot::plot_grid(plotlist = panels, ncol = grid_ncol, nrow = grid_nrow)
}, error = function(e) {
  ggplot() + annotate("text", x=.5, y=.5, label = paste("Error:", e$message), size=5, color="#999") + theme_void()
})}

make_xt_table <- function(q_prefix, group_var) {
  info <- var_dict %>% filter(var_prefix == q_prefix)
  qtype <- info$qtype[1]
  groups <- sort(unique(na.omit(dat_edit[[group_var]])))
  if (qtype %in% c("singleselect","derived")) {
    col <- get_stub(q_prefix, dat_edit)[1]
    dd <- dat_edit %>% filter(!is.na(.data[[col]]))
    overall <- dd %>% count(Option = .data[[col]]) %>%
      mutate(Overall = round(n/sum(n)*100)) %>% select(Option, Overall)
    by_g <- dd %>% filter(!is.na(.data[[group_var]])) %>%
      group_by(.data[[group_var]]) %>% mutate(n_g = n()) %>%
      count(Option = .data[[col]], n_g) %>% mutate(pct = round(n/n_g*100)) %>%
      ungroup() %>% select(!!group_var, Option, pct) %>%
      pivot_wider(names_from = !!group_var, values_from = pct, values_fill = 0)
    wide <- overall %>% left_join(by_g, by = "Option") %>% arrange(desc(Overall))
  } else {
    stbs <- get_stub(q_prefix, dat_edit); opts <- sub("^.*MULTISELECT \\| ", "", stbs)
    overall <- tibble(Option = opts,
      Overall = vapply(stbs, function(s) round(mean(dat_edit[[s]]=="Selected",na.rm=TRUE)*100), numeric(1)))
    by_g <- bind_rows(lapply(groups, function(g) {
      d_g <- dat_edit %>% filter(.data[[group_var]] == g)
      tibble(!!group_var := g, Option = opts,
        pct = vapply(stbs, function(s) round(mean(d_g[[s]]=="Selected",na.rm=TRUE)*100), numeric(1)))
    })) %>% pivot_wider(names_from = !!group_var, values_from = pct, values_fill = 0)
    wide <- overall %>% left_join(by_g, by = "Option") %>% arrange(desc(Overall))
  }
  wide <- wide %>% mutate(Option = stri_trans_general(Option, "Latin-ASCII"))
  num_cols <- names(wide)[sapply(wide, is.numeric)]
  disp <- wide; for (cc in num_cols) disp[[cc]] <- paste0(disp[[cc]], "%")
  names(disp)[1] <- ""
  k <- kbl(disp, format = "html", escape = TRUE, align = c("l", rep("r", length(num_cols)))) %>%
    kable_styling(bootstrap_options = c("striped","condensed"), font_size = 14, full_width = TRUE) %>%
    row_spec(0, bold = TRUE, background = "#f0ecf1", color = text_color)
  for (ci in seq_along(num_cols)) {
    vals <- wide[[num_cols[ci]]]; mx <- max(vals, na.rm = TRUE)
    if (mx > 0) { shades <- scales::col_numeric(c("#FFFFFF","#D4A5C4"), domain = c(0, mx))(vals)
      k <- column_spec(k, ci + 1, background = shades) }
  }
  k
}
```


## Research methodology {.q-slide}

:::: {.columns}
::: {.column width="44%"}

::: {.method-section}
**Project goals**

- Understand how B2C marketers plan, execute, and measure cultural moment marketing activations
- Assess readiness and activation plans for the 2026 FIFA World Cup and summer sporting events
- Evaluate AI adoption and its role in speed-to-market for cultural moments
- Measure channel coordination and personalization capabilities
- Identify barriers to faster activation and areas for investment
:::

::: {.method-section}
**Survey methodology**

A 33-question survey was designed by our data scientists and administered to 2,072 B2C marketers via Panoplai across 8 countries.

**Countries:** US (n=404), UK (n=435), France (n=213), Germany (n=207), Spain (n=205), Italy (n=200), Australia (n=203), Singapore (n=205)

**Fielding period:** March--April 2026
:::

:::

::: {.column width="4%"}
:::

::: {.column width="44%"}

::: {.method-section}
**Respondent profile**

B2C marketers with decision-making authority or influence over lifecycle marketing/CRM strategy at organizations with a direct-to-consumer presence.

Respondents were screened for active involvement in marketing strategy, with quotas set by country, vertical, and organization size.
:::

::: {.method-section}
**Crosstab notes**

- **Region:** APAC (n=408), EMEA (n=1,260), US (n=404)
- **Primary Vertical:** Apparel/fashion (n=284), Food/CPG (n=546), Health/sporting goods (n=215), Home goods (n=243), Multi-category (n=393), Other (n=391)
- **Size by GMV:** Enterprise (n=730), Non-enterprise (n=1,342)
:::

::: {.method-section}
**Project resources**

[Background analysis and content strategy](https://docs.google.com/document/d/1-0x4Qd_cvaWbFemKGGhjWAm_SqqVTc6xDYgzcQ82NSs/edit?usp=sharing){target="_blank" style="color: #4169E1;"}

[Survey design](https://docs.google.com/document/d/18QhPkN8K64RplmitD6GPOkLTGBurjOMaf3P0aeN5QLk/edit?usp=sharing){target="_blank" style="color: #4169E1;"}
:::

:::
::::


## Survey demographics: Sales channel model {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q1-")
```
:::
::::


## Survey demographics: Business model {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q2-")
```
:::
::::


## Survey demographics: Decision-making authority {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q3-")
```
:::
::::


## Survey demographics: Organizational role {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q4-")
```
:::
::::


## Survey demographics: Primary vertical {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q5-")
```
:::
::::


## Survey demographics: Organization size by GMV {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q6-")
```
:::
::::


## Research findings {.divider-blue}


## Cultural Moments: Which Moments Matter {.divider-orange}


## Only 27% of organizations have a dedicated cultural marketing team, while 25% have no clear ownership at all {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q7-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q7-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q7-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q7-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q7-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q7-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q7-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q7-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **US respondents are 37% more likely to report leadership decides on a case-by-case basis** compared to the overall average (26% vs. 19% overall)

2. **VP or Head of Marketing respondents are 54% more likely to say the broader marketing team owns cultural moments** compared to the overall average (40% vs. 26% overall)

3. **Both B2B and B2C companies are 15% more likely to have a dedicated cultural marketing team** than the overall average (31% vs. 27% overall)

4. **Founders/CEOs are 2.3x more likely to report no single owner or ad hoc cultural marketing** compared to the overall average (14% vs. 6% overall)

5. **APAC respondents are 12% more likely than the overall average to say the broader marketing team owns cultural moments alongside everything else** (29% vs. 26% overall)
:::
:::
::::

::: {.q-footer}
Q7: Who, in your organization, has primary ownership of cultural moment marketing? (n=2,072)
:::


## Nearly half (48%) of marketers activated around both planned and reactive cultural moments in the past year {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q8-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q8-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q8-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q8-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q8-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q8-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q8-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q8-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Apparel/fashion brands are 25% more likely to have activated around both planned and reactive moments** compared to the overall average (60% vs. 48% overall), the.

2. **Enterprise companies are 17% more likely to have activated around both planned and reactive moments** than the overall average (56% vs. 48% overall), and are far less.

3. **Both B2B and B2C companies are 13% more likely to have activated around both moment types** compared to the overall average (54% vs. 48% overall), while B2C-only firms.

4. **Founders/CEOs are 2.1x more likely to report no cultural moment activations** compared to the overall average (23% vs. 11% overall), while VP or Head of Marketing.

5. **APAC respondents are 15% more likely to have activated around both planned and reactive moments** compared to the overall average (55% vs. 48% overall), making them the.

6. **Health and sporting goods brands are 39% more likely than average to have focused mainly on planned moments** (43% vs. 31% overall), suggesting these brands lean toward.
:::
:::
::::

::: {.q-footer}
Q8: In the past 12 months, has your team intentionally built marketing activations around cultural moments? (n=2,072)
:::


## Regional/national sporting events (42%) and major music events (41%) lead as the most-activated planned cultural moments {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q9-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q9-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q9-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q9-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q9-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q9-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q9-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q9-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **US respondents are 21% more likely to have activated around major regional/national sporting events** compared to the overall average (51% vs. 42% overall), while APAC.

2. **Apparel/fashion brands are 2.2x more likely to have activated around fashion or style moments** like Met Gala or Fashion Weeks compared to the overall average (49% vs.

3. **C-Suite respondents are 36% more likely to have activated around major regional sporting events** than the overall average (57% vs. 42% overall), and are also 24% more.

4. **Enterprise companies are 22% more likely to have activated around global sporting events** compared to the overall average (45% vs. 37% overall), while non-enterprise.

5. **Both B2B and B2C companies are 10% more likely to have activated around major music events** compared to B2C-only firms (45% vs. 35%), and are also 24% more likely to.

6. **Multi-category retailers are 16% more likely to have activated around cultural awareness moments** compared to the overall average (44% vs. 38% overall), while Health.
:::
:::
::::

::: {.q-footer}
Q9: Which planned cultural moments has your team activated around in the past 12 months? (n=2,072)
:::


## Match Day: Sporting Events {.divider-orange}


## The 2026 FIFA World Cup dominates summer planning at 45%, far ahead of any other event {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q10-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q10-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q10-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q10-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q10-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q10-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q10-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q10-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **EMEA respondents are 9% more likely to be planning World Cup activations** compared to the overall average (49% vs. 45% overall), while APAC trails at 36%. EMEA also.

2. **APAC respondents are 2.2x more likely to be planning Commonwealth Games activations** compared to the overall average (29% vs. 13% overall) and are 57% more likely to be.

3. **Enterprise companies are 22% more likely to be planning World Cup activations** than the overall average (55% vs. 45% overall), and are 43% more likely to be planning.

4. **C-Suite respondents are 33% more likely to be planning World Cup activations** compared to the overall average (60% vs. 45% overall), the highest of any role segment.

5. **VP or Head of Marketing respondents are 53% more likely to be planning Tour de France activations** than the overall average (26% vs. 17% overall), and are 45% more.

6. **The "Other" vertical is the least likely to plan World Cup activations** at just 31% (vs. 45% overall -- 31% below average), and is 69% more likely to say they don't.
:::
:::
::::

::: {.q-footer}
Q10: Looking ahead to this summer, which events is your team planning to activate around? (n=2,072)
:::


## Time-sensitive offers triggered by match results (56%) and curated product drops (51%) lead World Cup activation plans {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q11-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q11-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q11-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q11-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q11-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q11-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q11-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q11-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Apparel/fashion brands are 37% more likely to plan curated product collections or limited-edition drops** tied to matches or teams compared to the overall average (70%.

2. **VP or Head of Marketing respondents are 38% more likely to plan personalized messaging** based on team or sport preferences compared to the overall average (44% vs. 32%.

3. **Enterprise companies are 26% more likely to plan AI-powered customer service** during events compared to the overall average (34% vs. 27% overall), and are 19% more.

4. **Both B2B and B2C companies are 19% more likely to plan AI-powered customer service** compared to B2C-only firms (32% vs. 18%), and are 30% more likely to plan curated.

5. **Multi-category retailers are 41% more likely to plan AI-powered customer service** during events compared to the overall average (38% vs. 27% overall), suggesting they.

6. **APAC respondents are 16% more likely to plan curated product collections** compared to the overall average (59% vs. 51% overall), while EMEA trails at 48%. All three.
:::
:::
::::

::: {.q-footer}
Q11: What types of activations are you planning around the World Cup and summer sporting events? (n=2,072)
:::


## International football tournaments (25%) are the top-performing sporting event, but the US is a stark outlier with American football dominating at 60% {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q12-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q12-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q12-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q12-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q12-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q12-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q12-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q12-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **US respondents overwhelmingly cite American football as the strongest-performing event** at 60%, which is 3.3x the overall rate of 18%. In contrast, international.

2. **EMEA respondents are 20% more likely to cite international football tournaments** as their top performer compared to the overall average (30% vs. 25% overall), and are.

3. **APAC respondents are 73% more likely to cite motorsport** as delivering the strongest results compared to the overall average (19% vs. 11% overall), and are the only.

4. **Health and sporting goods brands are 47% more likely to cite the Olympics** as their top-performing event compared to the overall average (25% vs. 17% overall), while.

5. **C-Suite respondents are 45% more likely to cite motorsport** as delivering the strongest results compared to the overall average (16% vs. 11% overall), and are also 30%.

6. **Enterprise companies are 12% more likely to cite international football tournaments** as their top performer compared to the overall average (28% vs. 25% overall), while.
:::
:::
::::

::: {.q-footer}
Q12: Which sporting event delivered the strongest marketing results for your brand in the past 12 months? (n=2,072)
:::


## Only 38% of teams are fully ready for the World Cup with plans, assets, and triggers in place {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q13-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q13-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q13-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q13-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q13-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q13-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q13-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q13-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Enterprise companies are 21% more likely to be fully ready** with plans, assets, and triggers in place compared to the overall average (46% vs. 38% overall), while.

2. **APAC respondents are the least fully prepared**, with only 31% reporting "Starting XI ready" status (vs. 38% overall -- 18% below average), while 55% are still building.

3. **Founders/CEOs are 32% more likely to be fully ready** compared to the overall average (50% vs. 38% overall), the highest of any role. In contrast, Directors/Managers and.

4. **Apparel/fashion brands are 26% more likely to be fully ready** compared to the overall average (48% vs. 38% overall), while Home goods brands are the least ready at 36%.

5. **B2C-only companies are 75% more likely to have no World Cup activation plans at all** compared to Both B2B and B2C firms (7% vs. 3%), and trail on full readiness (36%.

6. **Health and sporting goods brands are 11% more likely to still be building assets** compared to the overall average (50% vs. 45% overall), despite being a vertical with a.
:::
:::
::::

::: {.q-footer}
Q13: How prepared is your team to activate in time during the 2026 World Cup? (n=2,072)
:::


## Only 38% of teams are fully ready for the World Cup with plans, assets, and triggers in place {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q14-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q14-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q14-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q14-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q14-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q14-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q14-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q14-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Founders/CEOs are 58% more likely to plan a significant budget increase (>50%)** compared to the overall average (30% vs. 19% overall), the highest of any role segment.

2. **EMEA respondents are 11% more likely to plan a significant budget increase (>50%)** compared to the overall average (21% vs. 19% overall), while APAC trails at 16%. EMEA.

3. **Health and sporting goods brands are 23% more likely to plan a substantial (21-50%) budget increase** compared to the overall average (48% vs. 39% overall), the highest.

4. **Both B2B and B2C companies are 31% more likely to plan significant (>50%) budget increases** compared to B2C-only firms (21% vs. 16%), while B2C-only companies are 44%.

5. **The "Other" vertical is the most conservative on budget increases**, with the lowest rate of substantial increases (30% vs. 39% overall -- 23% below average) and the.

6. **Multi-category retailers are 26% more likely to plan significant (>50%) budget increases** compared to the overall average (24% vs. 19% overall), and Apparel/fashion.
:::
:::
::::

::: {.q-footer}
Q14: Will your team increase its marketing budget for summer sporting events compared to your typical always-on spend? (n=2,072)
:::


## Speed and Stakes {.divider-orange}


## 88% of teams plan to increase their marketing budget for summer sporting events, with 19% planning increases above 50% {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q15-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q15-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q15-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q15-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q15-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q15-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q15-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q15-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Founders are 42% more likely than the overall population to plan using AI for faster campaign production** (47% vs. 33% overall). This contrasts sharply with VPs or.

2. **C-Suite respondents are 16% more likely to plan AI-personalized messaging for sporting activations** (52% vs. 45% overall), suggesting senior leaders see personalization.

3. **VP or Head of Marketing respondents are 29% more likely to plan AI-powered customer service during event windows** (31% vs. 24% overall), the highest of any role segment.

4. **Enterprise respondents are 12% more likely than the overall population to use AI for faster campaign production** (37% vs. 33% overall), while non-enterprise brands.

5. **Health and sporting goods brands are 13% more likely to plan AI-personalized messaging** (51% vs. 45% overall), a natural fit given their direct connection to sporting.

6. **Apparel/fashion brands are 42% more likely than the overall population to use AI for faster campaign production** (47% vs. 33% overall), the highest of any vertical.
:::
:::
::::

::: {.q-footer}
Q15: Are you planning to use AI specifically to power your summer sporting activations? (n=2,072)
:::


## 45% of marketers plan to use AI for personalized messaging in summer sporting activations {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q16-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q16-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q16-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q16-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q16-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q16-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q16-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q16-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **APAC respondents are 18% more likely than the overall population to plan more than 6 months ahead** (26% vs. 22% overall), the most forward-planning region.

2. **C-Suite respondents are 13% more likely to have activations ready 3-6 months before** (43% vs. 38% overall), while Founders/CEOs are the least likely at 33% -- 13% below.

3. **Founders/CEOs are 100% more likely to launch the week of the event** (4% vs. 2% overall), suggesting smaller founder-led teams operate with tighter timelines.

4. **Enterprise brands are 18% more likely to plan more than 6 months ahead** (26% vs. 22% overall), while non-enterprise brands lag at 19%, reflecting longer enterprise.

5. **Health and sporting goods brands are 32% less likely to plan more than 6 months ahead** (15% vs. 22% overall), the lowest of any vertical, suggesting they rely on.

6. **B2C-only brands are 14% less likely to plan more than 6 months in advance** (19% vs. 22% overall) compared to Both B2B and B2C brands at 23%.
:::
:::
::::

::: {.q-footer}
Q16: How far ahead of a planned cultural moment (e.g. World Cup, Wimbledon) does your team typically have the activation ready to launch? (n=2,072)
:::


## 38% of teams have cultural moment activations ready 3-6 months in advance {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q17-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q17-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q17-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q17-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q17-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q17-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q17-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q17-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **US respondents are 56% more likely to be able to launch within 2 hours** (25% vs. 16% overall), far outpacing EMEA at just 13% -- making US teams nearly 2x as fast as.

2. **Founders/CEOs are 50% more likely to get a campaign live within 2 hours** (24% vs. 16% overall), likely reflecting shorter approval chains in founder-led organizations.

3. **Directors or Managers are 25% less likely than overall to launch within 2 hours** (12% vs. 16% overall), the slowest role segment, suggesting middle management faces.

4. **Home goods brands are 20% more likely to respond within 6 hours** (30% vs. 25% overall), the fastest vertical for this time window.

5. **Health and sporting goods brands are 31% less likely to respond within 2 hours** (11% vs. 16% overall), though they index higher at the 12-hour mark (25% vs. 22%.

6. **Non-enterprise brands are 12% more likely to respond within 6 hours** (28% vs. 25% overall), while enterprise brands lag at 23%, suggesting smaller organizations are.
:::
:::
::::

::: {.q-footer}
Q17: When an unexpected viral moment or cultural flashpoint hits, how quickly can your team get a campaign live? (n=2,072)
:::


## Only 16% of teams can launch a reactive campaign within 2 hours of an unexpected viral moment {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q18-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q18-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q18-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q18-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q18-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q18-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q18-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q18-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **US respondents are 53% more likely to have launched their most successful activation under 24 hours** (26% vs. 17% overall), more than double the EMEA rate of 16%.

2. **Founders/CEOs are 53% more likely to have achieved success with sub-24-hour turnarounds** (26% vs. 17% overall), reinforcing the speed advantage of founder-led teams.

3. **VPs or Heads of Marketing are 52% more likely to cite 4-7 day timelines for their best activation** (35% vs. 23% overall), suggesting VP-level teams operate in a.

4. **Health and sporting goods brands are 52% more likely to take 4-7 days** (35% vs. 23% overall), the highest of any vertical for this timeframe, while being 41% less.

5. **Enterprise brands are 25% more likely to take more than 2 weeks for their best activation** (10% vs. 8% overall), and 12% less likely to launch under 24 hours (15% vs.

6. **Non-enterprise brands are 12% more likely to have launched their best activation under 24 hours** (19% vs. 17% overall), confirming smaller brands' speed advantage.
:::
:::
::::

::: {.q-footer}
Q18: Thinking about your most successful cultural moment activation in the past 12 months: how long did it take from spotting the opportunity to launching the campaign? (n=2,072)
:::


## 37% of brands launched their most successful cultural moment activation within 1-3 days {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q19-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q19-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q19-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q19-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q19-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q19-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q19-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q19-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Health and sporting goods brands are 28% more likely to have missed 1-2 moments** (60% vs. 47% overall) and 29% less likely to have missed none (24% vs. 34% overall),.

2. **VPs or Heads of Marketing are 17% more likely to report missing 1-2 moments** (55% vs. 47% overall), the highest of any role, while being 24% less likely to report.

3. **APAC respondents are 6% more likely to have missed 1-2 moments** (50% vs. 47% overall), while US respondents are 15% more likely to report missing none (39% vs. 34%.

4. **Non-enterprise brands are 6% more likely to have missed 1-2 moments** (50% vs. 47% overall), while enterprise brands are 13% more likely to have missed 3-5 moments (17%.

5. **Founders/CEOs are 75% more likely to report missing more than 5 moments** (7% vs. 4% overall), the highest of any role segment for extreme misses.

6. **Multi-category retailers are 13% more likely to have missed 3-5 moments** (17% vs. 15% overall) and 25% more likely to miss more than 5 (5% vs. 4% overall), suggesting.
:::
:::
::::

::: {.q-footer}
Q19: In the past 12 months, how many cultural moments did your team miss because you couldn't move fast enough? (n=2,072)
:::


## 37% of brands launched their most successful cultural moment activation within 1-3 days {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q20-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q20-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q20-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q20-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q20-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q20-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q20-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q20-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Health and sporting goods brands are 15% more likely to attribute 10-20% of revenue to cultural moments** (61% vs. 53% overall), the highest of any vertical.

2. **Apparel/fashion brands are 29% more likely to report more than 20% of revenue from cultural moments** (27% vs. 21% overall), the highest vertical for top-tier revenue.

3. **VP or Head of Marketing respondents are 12% more likely to report 10-20% revenue attribution** (59% vs. 53% overall), while Founders/CEOs are 17% less likely at 44%.

4. **Founders/CEOs are 19% more likely to report more than 20% of revenue from cultural moments** (25% vs. 21% overall), the highest of any role, suggesting founder-led.

5. **Enterprise brands are 14% more likely to attribute more than 20% of revenue to cultural moments** (24% vs. 21% overall) compared to 19% for non-enterprise brands.

6. **Both B2B and B2C brands are 35% more likely to attribute more than 20% of revenue** (23% vs. 17% for B2C-only), while B2C-only brands are 30% more likely to not measure.
:::
:::
::::

::: {.q-footer}
Q20: Approximately what share of your total marketing revenue comes from cultural moment activations vs. routine calendar marketing? (n=2,072)
:::


## Channels, Data, and Personalization {.divider-orange}


## Two-thirds (66%) of teams missed at least one cultural moment in the past year due to speed {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q21-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q21-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q21-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q21-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q21-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q21-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q21-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q21-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Health and sporting goods brands are 16% more likely to assess cultural moments case-by-case** (73% vs. 63% overall), the highest of any vertical, while being 25% less.

2. **VP or Head of Marketing respondents are 11% more likely to assess case-by-case** (70% vs. 63% overall), while Founders/CEOs are 11% less likely (56% vs. 63% overall).

3. **Founders/CEOs are 18% more likely to have clear brand guidelines** (33% vs. 28% overall) but also 100% more likely to make decisions based on gut calls (6% vs. 3%.

4. **Enterprise brands are 21% more likely to have clear brand guidelines** (34% vs. 28% overall) compared to 25% for non-enterprise brands, reflecting more formalized.

5. **Non-enterprise brands are 33% more likely to rely on gut calls** (4% vs. 3% overall) and just 1% for enterprise, suggesting smaller brands lack formal frameworks.

6. **Both B2B and B2C brands are 7% more likely to have clear brand guidelines** (30% vs. 28% overall) compared to B2C-only at 25%, while B2C-only brands are 33% more likely.
:::
:::
::::

::: {.q-footer}
Q21: How does your team decide whether or not it has a credible reason to participate in a cultural moment? (n=2,072)
:::


## Over half (53%) attribute 10-20% of marketing revenue to cultural moment activations {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q22-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q22-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q22-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q22-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q22-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q22-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q22-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q22-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Apparel/fashion brands are 17% more likely to cite social media as their best channel** (54% vs. 46% overall), the highest of any vertical, reinforcing social's.

2. **US respondents are 80% more likely to cite SMS as their best-performing channel** (9% vs. 5% overall), while EMEA is 40% less likely at just 3%, reflecting different.

3. **EMEA respondents are 30% more likely to cite WhatsApp as a top channel** (13% vs. 10% overall), while the US is 70% less likely at just 3%, reflecting WhatsApp's.

4. **Health and sporting goods brands are 80% more likely to cite WhatsApp as their best channel** (18% vs. 10% overall), the highest of any vertical.

5. **VP or Head of Marketing respondents are 60% more likely to cite influencer or creator partnerships** (16% vs. 10% overall), the highest of any role, while Founders/CEOs.

6. **Enterprise brands are 43% more likely to cite ads (TV, YouTube, Podcasts) as their best channel** (10% vs. 7% overall), reflecting larger media budgets, compared to just.
:::
:::
::::

::: {.q-footer}
Q22: Which channel delivers the best results for your cultural moment activations? (n=2,072)
:::


## 63% of teams assess cultural moment participation case-by-case rather than using formal guidelines {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q23-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q23-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q23-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q23-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q23-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q23-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q23-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q23-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Founders and CEOs are 18% more likely than average to report full coordination** across channels during cultural moments (47% vs. 40% overall), suggesting senior leaders.

2. **Directors and Managers are 12% more likely to say channels are only "mostly coordinated"** rather than fully coordinated (57% vs. 51% overall), while being 18% less.

3. **Apparel/fashion brands are 25% more likely to claim full coordination** compared to the overall average (50% vs. 40% overall), the highest rate of any vertical.

4. **"Other" vertical respondents are 71% more likely to say channels operate independently** (12% vs. 7% overall), suggesting less-defined verticals struggle more with.

5. **Enterprise companies are 13% more likely to report full coordination** than the overall average (45% vs. 40% overall), while non-enterprise companies lag at 37%.

6. **Both B2B and B2C businesses are 5% more likely than B2C-only to report full coordination** (42% vs. 37%), possibly reflecting more mature orchestration infrastructure.
:::
:::
::::

::: {.q-footer}
Q23: In your opinion, how coordinated are your channels when you activate around a cultural moment? (n=2,072)
:::


## Social media dominates as the top cultural moment channel at 46%, nearly 3x the next channel {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q24-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q24-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q24-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q24-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q24-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q24-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q24-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q24-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **US respondents are 17% more likely to be very confident in their targeting** compared to the overall average (48% vs. 41% overall), while APAC trails at 37% -- a gap of.

2. **Enterprise companies are 20% more likely than average to report high confidence** in personalized targeting (49% vs. 41% overall), compared to just 36% for.

3. **Apparel/fashion brands are 20% more likely to be very confident** in reaching the right customers (49% vs. 41% overall), the highest of any vertical.

4. **Health and sporting goods respondents are 24% less likely to report high confidence** (31% vs. 41% overall) and are 18% more likely to say they only segment without true.

5. **C-Suite executives are 22% more likely than average to be very confident** in their targeting precision (50% vs. 41% overall), while Directors/Managers are the least.

6. **Both B2B and B2C businesses are 16% more likely to report high confidence** compared to B2C-only firms (43% vs. 37%), suggesting dual-model companies invest more in.
:::
:::
::::

::: {.q-footer}
Q24: When you activate around a cultural moment, how confident are you that your team is reaching the right customers with the right message? (n=2,072)
:::


## The AI Advantage {.divider-orange}


## 91% of marketers say their channels are at least mostly coordinated around cultural moments {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q25-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q25-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q25-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q25-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q25-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q25-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q25-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q25-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **APAC respondents are 17% more likely to prioritize faster access to real-time customer data** over the overall average (35% vs. 30% overall), making it their top choice.

2. **Health and sporting goods marketers are 20% more likely to choose AI-assisted content creation** (42% vs. 35% overall), the highest of any vertical.

3. **Multi-category retailers are 20% more likely to prioritize real-time customer data** (36% vs. 30% overall) and are 41% less likely to want streamlined approvals (10% vs.

4. **APAC is 18% more likely than average to cite streamlined internal approvals** as a top accelerator (20% vs. 17% overall), while US respondents are 24% less likely to.

5. **Founders/CEOs are 41% less likely to want streamlined approvals** (10% vs. 17% overall) but are 20% more likely to prioritize real-time customer data (36% vs. 30%.

6. **VPs/Heads of Marketing are 24% more likely to want streamlined internal approvals** (21% vs. 17% overall), the highest of any role, suggesting they face the most.
:::
:::
::::

::: {.q-footer}
Q25: What would most help your team halve the time it takes to launch a cultural moment activation? (n=2,072)
:::


## Only 41% of marketers are "very confident" they reach the right customers with the right message during cultural moments {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q26-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q26-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q26-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q26-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q26-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q26-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q26-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q26-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **US respondents are 75% more likely to say they don't use AI at all** for cultural moment activations (14% vs. 8% overall), while APAC is 25% less likely to say the same.

2. **Enterprise companies are 25% more likely to use AI-powered customer service** during event windows (25% vs. 20% overall) and 21% more likely to build full campaigns from.

3. **Founders/CEOs are 21% more likely to use AI for content generation** (51% vs. 42% overall), the highest rate of any role, but are 63% more likely to report not using AI.

4. **C-Suite executives are 36% more likely to use AI for audience segmentation** (45% vs. 33% overall), the highest segmentation adoption among all roles.

5. **B2C-only companies are 50% more likely to not use AI at all** compared to Both B2B and B2C firms (12% vs. 6%), while B2B+B2C companies lead in every AI use case.

6. **Both B2B and B2C companies are 44% more likely to use AI-powered customer service** than B2C-only firms (23% vs. 16%), suggesting dual-model businesses find more value.
:::
:::
::::

::: {.q-footer}
Q26: How does your team currently use AI or automation for cultural moment activations? (n=2,072)
:::


## AI-assisted content creation is the top accelerator for cultural moment activations, chosen by 35% {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q27-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q27-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q27-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q27-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q27-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q27-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q27-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q27-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Directors and Managers are 13% more likely to be positive about vibe marketing** (61% vs. 54% overall), while Founders/CEOs are 26% less likely to be positive (40% vs.

2. **Founders/CEOs are 75% more likely to be skeptical about vibe marketing** than average (14% vs. 8% overall), the highest skepticism rate of any role, compared to just 2%.

3. **Enterprise companies are 20% more likely to already be practicing vibe marketing** compared to non-enterprise (30% vs. 23%), while non-enterprise firms are 67% more.

4. **B2C-only companies are 38% more likely to be skeptical** about vibe marketing compared to Both B2B and B2C firms (11% vs. 6%), and 38% more likely to be unsure (15% vs.

5. **Both B2B and B2C firms are 38% more likely to already be doing vibe marketing** compared to B2C-only firms (29% vs. 21%).

6. **APAC respondents are 11% more likely to feel positive** about vibe marketing (60% vs. 54% overall) and 31% less likely to be unsure (9% vs. 13% overall), showing the.
:::
:::
::::

::: {.q-footer}
Q27: Some teams now define the outcome they want and let AI generate the content, audience, and launch the activation automatically - sometimes called "vibe marketing." How do you feel about this? (n=2,072)
:::


## Performance and Confidence {.divider-orange}


## 42% of teams use AI for content generation in cultural moment activations, but 8% don't use AI at all {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q28-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q28-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q28-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q28-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q28-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q28-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q28-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q28-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **US respondents are 45% more likely to measure both commercial and brand building** compared to the overall average (45% vs. 31% overall), while EMEA is the most likely.

2. **VPs/Heads of Marketing are 26% more likely to prioritize brand building metrics** (54% vs. 43% overall), the highest of any role, while Founders/CEOs are 16% less likely.

3. **Health and sporting goods brands are 14% more likely to prioritize brand building** (49% vs. 43% overall), the highest vertical rate, while Apparel/fashion is the most.

4. **Both B2B and B2C companies are 6% more likely to use a dual measurement approach** (33% vs. 28% for B2C-only), while B2C-only firms are 13% more likely to focus on pure.

5. **Enterprise and non-enterprise companies measure cultural moments nearly identically** on brand building (42% vs. 43%), though Enterprise is slightly more likely to use a.

6. **APAC respondents are 9% more likely to prioritize brand building** (47% vs. 43% overall), while US respondents are 16% less likely to focus on brand building alone (36%.
:::
:::
::::

::: {.q-footer}
Q28: What is your primary measure of success for cultural moment activations? (n=2,072)
:::


## 42% of teams use AI for content generation in cultural moment activations, but 8% don't use AI at all {.q-slide}

:::: {.columns}
::: {.column width="62%"}

```{=html}
<div class="xt-nav">
  <a href="javascript:void(0)" data-xt="overall" class="active">Overall</a>
  <a href="javascript:void(0)" data-xt="region">By Region</a>
  <a href="javascript:void(0)" data-xt="vertical">By Vertical</a>
  <a href="javascript:void(0)" data-xt="size">By Size</a>
</div>
```

::: {.pane data-xt="overall" data-view="chart"}
```{r}
#| fig-width: 10
#| fig-height: 8
make_bar("Q29-")
```
:::

::: {.pane data-xt="overall" data-view="table" .pane-hidden}
```{r}
make_table("Q29-")
```
:::

::: {.pane data-xt="region" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q29-", "region")
```
:::

::: {.pane data-xt="region" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q29-", "region")
```
:::



::: {.pane data-xt="vertical" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q29-", "primary_vertical")
```
:::

::: {.pane data-xt="vertical" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q29-", "primary_vertical")
```
:::

::: {.pane data-xt="size" data-view="chart" .pane-hidden}
```{r}
#| fig-width: 12
#| fig-height: 7.5
make_grid("Q29-", "size_by_gmv")
```
:::

::: {.pane data-xt="size" data-view="table" .pane-hidden}
```{r}
make_xt_table("Q29-", "size_by_gmv")
```
:::

```{=html}
<div class="view-nav">
  <a href="javascript:void(0)" data-view="chart" class="active">Chart</a>
  <a href="javascript:void(0)" data-view="table">Table</a>
</div>
```

:::

::: {.column width="38%"}
::: {.insights-panel}
::: {.insights-label}
Key takeaways
:::

1. **Apparel/fashion brands are 19% more likely to say cultural moments outperform** routine calendar marketing (44% vs. 37% overall), the highest of any vertical, while.

2. **Enterprise companies are 14% more likely to report cultural moments outperforming** routine marketing (42% vs. 37% overall), compared to 34% for non-enterprise -- a.

3. **Both B2B and B2C companies are 25% more likely than B2C-only to say cultural moments outperform** (40% vs. 32%), suggesting that businesses with more complex customer.

4. **VPs/Heads of Marketing are 11% more likely to report outperformance** (41% vs. 37% overall), while Directors/Managers are 8% less likely (34% vs. 37% overall) -- the.

5. **US respondents are 11% less likely to report cultural moment outperformance** (33% vs. 37% overall) and are the most likely region to say performance is "about the same".

6. **APAC respondents are 29% more likely to say cultural moments underperform** (9% vs. 7% overall), the highest underperformance rate of any region.
:::
:::
::::

::: {.q-footer}
Q29: Compared to your routine calendar marketing (e.g. Black Friday, Cyber Monday, holiday), how do cultural moment activations perform? (n=2,072)
:::


## 79% of marketers are positive about or already practicing "vibe marketing" with AI-driven activations {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q31-")
```
:::
::::


## 79% of marketers are positive about or already practicing "vibe marketing" with AI-driven activations {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q32-")
```
:::
::::


## 79% of marketers are positive about or already practicing "vibe marketing" with AI-driven activations {.q-slide}
:::: {.columns}
::: {.column width="100%"}
```{r}
#| fig-width: 14
#| fig-height: 8
make_bar("Q33-")
```
:::
::::


## Thank you {.thankyou}

HELLO@DATALILY.COM
